Impact of Isotope Fidelity on Fuel Cycle Calculations

### 2016-08-09 paper.tex
addresing minor issues

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[width=0.48\textwidth]{flow}
  \caption{Schematic representation of the fuel cycle. Quantities on the row
  represents the cumulative amount in kg of material exchanged between two
  facilities in the calculation using ``pu-equivalent'' for fuel fabrication
  modeling with decay activated.}
  \label{fig:flow}
\end{figure}

@@

With decay turned on, see Fig. \ref{fig:d}, results for the ``fix mixing ratio''
calculation see a small decrease of the fraction of plutonium in the fuel,
corresponding to the decay of $^{241}$Pu into $^{241}$Am.  For the
``Pu-equivalent'' modeling we can observe a slight increase of the fraction of
plutonium, which is required to compensate for the negative reactivity effect
coming from the $^{241}$Am. For the calculation using ``neural network'' fuel
fabrication modeling the effect is very quickly increasing to $13\%$ and then
slowing stabilizing as the plutonium composition approaches an equilibrium.

@@

%% PPHW: why is the Pu-equiavlent model so bad?

>>>>

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[width=0.48\textwidth]{flow}
  \caption{Schematic representation of the fuel cycle. Quantities on the row
  represent the cumulative amount in kg of material exchanged between two
  facilities in the calculation using ``pu-equivalent'' for fuel fabrication
  modeling with decay activated.}
  \label{fig:flow}
\end{figure}

@@

With decay turned on, see Fig. \ref{fig:d}, results for the ``fix mixing ratio''
calculation see a small decrease of the fraction of plutonium in the fuel,
corresponding to the decay of $^{241}$Pu into $^{241}$Am.  For the
``Pu-equivalent'' modeling we can observe a slight increase of the fraction of
plutonium, which is required to compensate for the negative reactivity effect
coming from the $^{241}$Am. For the calculation using ``neural network'' fuel
fabrication modeling the effect very quickly increases to $13\%$ and then
slowing stabilizing as the plutonium composition approaches an equilibrium.

@@
